Limma Tutorial

### 2018-04-13 C_R/DESeq2/makeDataMetrics.Rmd
Venn updates

>>>>

    sigMetrics <- metrics[which(metrics$padj <0.05),]
    RDC <- sigMetrics[which(sigMetrics$log2FoldChange>0),]$ID
    RDR <- sigMetrics[which(sigMetrics$log2FoldChange<0),]$ID
    RD_DIET_TOTAL <- metrics[which(metrics$padj <0.05),]$ID

    saveRDS(RDC, file="RDC.Rds")
    saveRDS(RDR, file="RDR.Rds")
    saveRDS(RD_DIET_TOTAL, file="RD_DIET_TOTAL.Rds")

### 2018-04-13 C_R/LimmaVoom/makeDataMetrics.Rmd
Count RDS files diet and virus
Venn updates

```{r}
summary(decideTests(efit))
```

>>>>

```{r}
summary(decideTests(efit))
countDF <- as.data.frame(decideTests(efit)@.Data)
RLC <- rownames(countDF)[which(countDF==1)]
RLR <- rownames(countDF)[which(countDF==-1)]
RL_DIET_TOTAL <- c(RLC, RLR)

saveRDS(RLC, file="RLC.Rds")
saveRDS(RLR, file="RLR.Rds")
saveRDS(RL_DIET_TOTAL, file="RL_DIET_TOTAL.Rds")
```

### 2018-04-13 N_V/DESeq2/makeDataMetrics.Rmd
Venn updates

    RDC <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange>0),]$ID
    RDR <- metrics[which(metrics[which(metrics$padj <0.05),]$log2FoldChange<0),]$ID
    RD_DIET <- metrics[which(metrics$padj <0.05),]$ID
    saveRDS(RDC, file="RDC.Rds")
    saveRDS(RDR, file="RDR.Rds")
    saveRDS(RD_DIET, file="RD_DIET.Rds")

>>>>

    sigMetrics <- metrics[which(metrics$padj <0.05),]
    RDN <- sigMetrics[which(sigMetrics$log2FoldChange>0),]$ID
    RDV <- sigMetrics[which(sigMetrics$log2FoldChange<0),]$ID
    RD_VIRUS_TOTAL <- metrics[which(metrics$padj <0.05),]$ID

    saveRDS(RDV, file="RDV.Rds")
    saveRDS(RDN, file="RDN.Rds")
    saveRDS(RD_VIRUS_TOTAL, file="RD_VIRUS_TOTAL.Rds")

### 2018-04-13 VirusHoneyBee/EdgeR/edgeR/makeDataMetrics.Rmd
Venn updates

>>>>

    GEC1 <- rownames(lrt5[which(lrt5$logFC>0),])
    GEV1 <- rownames(lrt5[which(lrt5$logFC<0),])
    GE_VIRUS1 <- rownames(lrt5)

    GEC <- unname(sapply(GEC1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GEV <- unname(sapply(GEV1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
    GE_TOTAL <- unname(sapply(GE_TOTAL1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))

    saveRDS(GEC, file="GEC.Rds")
    saveRDS(GEV, file="GEV.Rds")
    saveRDS(GE_TOTAL, file="GE_TOTAL.Rds")

### 2018-04-13 VirusHoneyBee/LimmaVoom/makeDataMetrics.Rmd
Venn updates

```{r}
summary(decideTests(efit))
```

>>>>

```{r}
summary(decideTests(efit))

countDF <- as.data.frame(decideTests(efit)@.Data)
GLC1 <- rownames(countDF)[which(countDF==1)]
GLV1 <- rownames(countDF)[which(countDF==-1)]
GL_TOTAL1 <- c(GLC1, GLV1)

GLC <- unname(sapply(GLC1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
GLV <- unname(sapply(GLV1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))
GL_TOTAL <- unname(sapply(GL_TOTAL1, function(x) strsplit(strsplit(x, "[|]")[[1]][3], "[-]")[[1]][1]))

saveRDS(GLC, file="GLC.Rds")
saveRDS(GLV, file="GLV.Rds")
saveRDS(GL_TOTAL, file="GL_TOTAL.Rds")

```
